---
title: "State Constitution Analysis"
subtitle: "Project 2"
author: "Cassie Minicucci, Katie Riley, and Basil-Anne Stackpole"
title-slide-attributes:
  data-slide-number: none
format: revealjs
editor: visual
execute:
  echo: false
---

```{r}
#| label: load-packages
#| include: false

library(tidyverse)
```

```{r}
#| label: setup
#| include: false

# For better figure resolution
knitr::opts_chunk$set(
  fig.retina = 3, 
  dpi = 300, 
  fig.width = 6, 
  fig.asp = 0.618, 
  out.width = "70%"
  )
```

```{r}
#| label: load-data
#| include: false
```

## Does the time a state came into being affect the keywords used in its Constitution?

We scraped text from the constitutions of the original 13 colonies and analyzed each for specific keywords.

-   Keywords: freedom, liberty, welfare, consent, prohibit, equality, and rights

## Does the time a state came into being affect the keywords used in its Constitution?

Then, we created an interactive map using a time variable to be able to see when each state was ratified.

Goal: to understand if the time a state was ratified has a large effect on the language used in the constitution.

## Game plan

-   Scrape text from each constitution and create separate dataframes for each
-   Find frequencies of each keyword in each constitution
-   Link dataframes together into one dataframe to create interactive map
-   Create interactive map!

## Ratification years {.smaller}

| state  | year   |
|--------|--------|
| Delaware  | 1787 |
| Georgia   | 1777  |
| Connecticut | 1776 |
| Maryland  | 1776  |
| Massachusetts   | 1780  |
| New Hampshire | 1776   |
| New Jersey  | 1776   |
| New York   | 1777   |
| North Carolina | 1776   |
| Pennsylvania  | 1776   |
| Rhode Island   | 1843   |
| South Carolina | 1778   |
| Virginia | 1776 |


## Keyword frequencies: Delaware
Ratification year: 1787

insert histogram here

## Keyword frequencies: Georgia
Ratification year: 1777

## Keyword frequencies: Connecticut
Ratification year: 1776

## Keyword frequencies: Maryland
Ratification year: 1776

## Keyword frequencies: Massachusetts
Ratification year: 1780

## Keyword frequencies: New Hampshire
Ratification year: 1776

## Keyword frequencies: New Jersey
Ratification year: 1776

## Keyword frequencies: New York
Ratification year: 1777

## Keyword frequencies: North Carolina
Ratification year: 1776

## Keyword frequencies: Pennsylvania
Ratification year: 1776

## Keyword frequencies: Rhode Island
Ratification year: 1843

## Keyword frequencies: South Carolina
Ratification year: 1778

## Keyword frequencies: Virginia
Ratification year: 1776

## Interactive maps


## Conclusions
- something cool about the frequencies
- something cool about the maps
- smart closing sentence
