---
title: "State Constitution Analysis"
subtitle: "Project 2"
author: "Cassie Minicucci, Katie Riley, and Basil-Anne Stackpole"
title-slide-attributes:
  data-slide-number: none
format: revealjs
editor: visual
execute:
  echo: false
---

```{r}
#| label: load-packages
#| include: false

library(tidyverse)
```

```{r}
#| label: setup
#| include: false

# For better figure resolution
knitr::opts_chunk$set(
  fig.retina = 3, 
  dpi = 300, 
  fig.width = 6, 
  fig.asp = 0.618, 
  out.width = "70%"
  )
```

```{r}
#| label: load-data
#| include: false
```

## Does the time a state came into being affect the keywords used in its Constitution?
We scraped text from the constitutions of the original 13 colonies and analyzed each for specific keywords.

* Keywords: freedom, liberty, welfare, consent, prohibit, equality, and rights

## Does the time a state came into being affect the keywords used in its Constitution?

Then, we created an interactive map using a time variable to be able to see when each state was ratified.

Goal: to understand if the time a state was ratified has a large effect on the language used in the constitution.

## Game plan
* Scrape text from each constitution and create separate dataframes for each
* Find frequencies of each keyword in each constitution
* Link dataframes together into one dataframe to create interactive map
* Create interactive map!

## Ratification years

dataframe of state to year ratified



## Keyword frequency



## Interactive map









