---
title: "Project 2 - State Constitution Analysis"
subtitle: "Proposal"
authors: "Katie Riley, Basil-Anne Stackpole, and Cassie Minicucci"
format: html
editor: visual
---

```{r load-packages}
#| label: load-pkgs
#| message: false
#| warning: false

library(tidyverse)
```

## Dataset

```{r load-data}
#| label: load-data
#| message: false

## read data 
```

## Reason for Choosing this Dataset

**Our Project: We intend to examine the United States's individual state constitutions for the frequency of specific keywords and visualize these onto an interactive map of the United States which allows the user to adjust for time, beginning with the 13 colonies and adding more states as time continues and more states are formed.**

## Questions and Analysis Plan

**Research question:** Does the time a state came into being affect the keywords used in its Constitution?

## In-depth proposal and motivations:

In order to better understand the political and legal differences within states, especially the differences between the states that were a part of the original thirteen colonies and those who were not, we aim to analyze the constitutions of all fifty US states for certain keywords: "freedom," "liberty," "welfare," "consent," "prohibit," "equality," and "rights." Once we ascertain the frequency of these keywords within each constitution, we will create seven different maps of the United States (one for each keyword) colored by the frequency of the keyword. This will help us understand the way language is used in different state constitutions. We will then make these maps interactive using the variable of time; we hope to use the time scale to show when different states came into being, starting with the original thirteen colonies. This will help us understand if the time a state was ratified has a large effect on the language used in the constitution. 

=======
## Weekly "plan of attack"

Week 1 (April 7th -13th)

-   Establish a process to scrape the individual constitutions from state government websites and convert them into tidy data frames, excluding all text from the website not in the constitution (Basil-Anne)

-   Replicate this process for all 50 states (Each team member uses the process finalized in the previous step to complete a portion of the states, each person will be responsible for at least 15 states)

-   Run analysis on each new dataset using the key words (this will be the same process as the previous step where each team member takes a portion of the states and follows the same procedure)

    -   This should result in data frames for each state with columns indicating the appearances of each keyword

Week 2 (14th - 20th)

-   Join the separate state data frames into one dataframe using the key words (Basil-Anne)

-   Create interactive maps for the 7 key words (each team member will take 2 maps following the same workflow)

-   Begin working on Presentation Slides (Katie)

Week 3 (April 21st - 27th)

-   Finish presentation slides using the interactive maps (Katie with help from other team members)

-   Complete write up of the project (Cassie)

-   Create Website with interactive maps and write up (Katie)

## Project organization of project repository

*As we are creating a website, we will need an index.qmd, a quarto.yml, and an about.qmd. We will have links to all portions of the project (proposal, presentation, write-up, and page with interactive maps) within the website, accessible within a tab; these will also be within the repo in qmd files. Within the repository, these pages are all easily accessible in the code panel; none are within specific folders. We will eventually have a "data" folder with all datasets once they have been located, scraped, and wrangled, as learning the techniques for doing this will be the meat of our project. Aesthetically, the final website will have a tab at the top for accessing other portions of the project, and the interactive maps will either be on the front page or within one of the said tabs. The front page could also be an intro to our project.
