---
title: "State_constitutions"
format: html
editor: visual
---

## List Of States

Connecticut (Basil-Anne)

Delaware: <https://avalon.law.yale.edu/18th_century/de02.asp> (Basil-Anne)

Georgia: <https://avalon.law.yale.edu/18th_century/ga02.asp> (Katie)

Maryland: <https://avalon.law.yale.edu/17th_century/ma02.asp> (Katie)

Massachusetts: (Basil-Anne)

New Hampshire: <https://avalon.law.yale.edu/18th_century/nh09.asp> (Katie)

New Jersey: <https://avalon.law.yale.edu/18th_century/nj15.asp> (Katie)

New York: <https://avalon.law.yale.edu/18th_century/ny01.asp> (Cassie)

North Carolina: <https://avalon.law.yale.edu/18th_century/nc07.asp> (Cassie)

Pennsylvania: <https://avalon.law.yale.edu/18th_century/pa08.asp> (Cassie)

Rhode Island: (Basil-Anne)

South Carolina: <https://avalon.law.yale.edu/18th_century/sc02.asp> (Cassie)

Virginia: (Basil-Anne)

## Connecticut

```{r}

```

## Delaware

```{r}
library(rvest)
library(dplyr)

de_url <- "https://avalon.law.yale.edu/18th_century/de02.asp"
de_html <- read_html(de_url)

de_text <- html_text(de_html)

de_con <- data.frame(word = unlist(strsplit(de_text, "\\s+"))) %>%
  filter(word != "")  

rows_to_exclude <- c(1:54, 3721:3796)

de_con_tidy <- de_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))

```

## Georgia

```{r}

```

## Maryland

```{r}

```

## Massachusetts

```{r}

```

## New Hampshire

```{r}

```

## New Jersey

```{r}

```

## New York

```{r}

```

## North Carolina

```{r}

```

## Pennsylvania

```{r}

```

## Rhode Island

```{r}

```

## South Carolina

```{r}

```

## Virginia

```{r}

```

## 
