---
title: "State_constitutions"
format: html
editor: visual
---

## List Of States

Connecticut: <https://www.cga.ct.gov/asp/Content/constitutions/1818Constitution.htm> (Basil-Anne)

Delaware: <https://avalon.law.yale.edu/18th_century/de02.asp> (Basil-Anne)

Georgia: <https://avalon.law.yale.edu/18th_century/ga02.asp> (Katie)

Maryland: <https://avalon.law.yale.edu/17th_century/ma02.asp> (Katie)

Massachusetts: <http://www.nhinet.org/ccs/docs/ma-1780.htm> (Basil-Anne)

New Hampshire: <https://avalon.law.yale.edu/18th_century/nh09.asp> (Katie)

New Jersey: <https://avalon.law.yale.edu/18th_century/nj15.asp> (Katie)

New York: <https://avalon.law.yale.edu/18th_century/ny01.asp> (Cassie)

North Carolina: <https://avalon.law.yale.edu/18th_century/nc07.asp> (Cassie)

Pennsylvania: <https://avalon.law.yale.edu/18th_century/pa08.asp> (Cassie)

Rhode Island: <https://www.wordservice.org/State%20Constitutions/usa1031.htm> (Basil-Anne)

South Carolina: <https://avalon.law.yale.edu/18th_century/sc02.asp> (Cassie)

Virginia: <https://www.wordservice.org/State%20Constitutions/usa1025.htm> (Basil-Anne)

## Connecticut

```{r}
library(rvest)
library(dplyr)
ct_url <- "https://www.cga.ct.gov/asp/Content/constitutions/1818Constitution.htm"
ct_html <- read_html(ct_url)

ct_text <- html_text(ct_html)

ct_con <- data.frame(word = unlist(strsplit(ct_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude_ct <- c(1:7, 223:298, 6012:12230)

ct_con_tidy <- ct_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude_ct))

```

```{r}
library(tidyverse)
library(tidytext)
ct_word_count <- ct_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
ct_con_tidy_nostop <- ct_con_tidy %>%
 anti_join(stop_words) 
ct_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) 
#WHY U HAVE SPACE
```

## Delaware

```{r}
library(rvest)
library(dplyr)

de_url <- "https://avalon.law.yale.edu/18th_century/de02.asp"
de_html <- read_html(de_url)

de_text <- html_text(de_html)

de_con <- data.frame(word = unlist(strsplit(de_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude <- c(1:54, 3721:3796)

de_con_tidy <- de_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))

```

```{r}
library(tidyverse)
library(tidytext)
de_word_count <- de_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
de_con_tidy_nostop <- de_con_tidy %>%
 anti_join(stop_words) 
de_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) 
```

## Georgia

```{r}
library(rvest)
library(dplyr)

ga_url <- "https://avalon.law.yale.edu/18th_century/ga02.asp"
ga_html <- read_html(ga_url)

ga_text <- html_text(ga_html)

ga_con <- data.frame(word = unlist(strsplit(ga_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude_ga <- c(1:56, 4422:4652)

ga_con_tidy <- ga_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude_ga))

```

```{r}
library(tidyverse)
library(tidytext)
ga_word_count <- ga_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
ga_con_tidy_nostop <- ga_con_tidy %>%
 anti_join(stop_words) 
ga_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) 
```

## Maryland

```{r}
library(rvest)
library(dplyr)

md_url <- "https://avalon.law.yale.edu/17th_century/ma02.asp"
md_html <- read_html(md_url)

md_text <- html_text(md_html)

md_con <- data.frame(word = unlist(strsplit(md_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude_md <- c(1:94, 2623:2669, 8854:9084)

md_con_tidy <- md_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude_md))
```

```{r}
library(tidyverse)
library(tidytext)
md_word_count <- md_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
md_con_tidy_nostop <- md_con_tidy %>%
 anti_join(stop_words) 
md_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) 
```

## Massachusetts

```{r}
ma_url <- "http://www.nhinet.org/ccs/docs/ma-1780.htm "
ma_html <- read_html(ma_url)

ma_text <- html_text(ma_html)

ma_con <- data.frame(word = unlist(strsplit(ma_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude_ma <- c(11433:11445)

ma_con_tidy <- ma_con %>%
  mutate(word = tolower(word)) %>%
  mutate(word=gsub("[[:space:]]", "", word)) %>%
  filter(!(row_number() %in% rows_to_exclude_ma))

```

```{r}
library(tidyverse)
library(tidytext)
ma_word_count <- ma_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
ma_con_tidy_nostop <- ma_con_tidy %>%
 anti_join(stop_words) 
ma_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) %>%
  filter(!word%in%c("(art.", ""))
#wTHIS IS FUCKED UP
```

## New Hampshire

```{r}
library(rvest)
library(dplyr)

nh_url <- "https://avalon.law.yale.edu/18th_century/nh09.asp"
nh_html <- read_html(nh_url)

nh_text <- html_text(nh_html)

nh_con <- data.frame(word = unlist(strsplit(nh_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude_nh <- c(1:63, 994:1242)

nh_con_tidy <- nh_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude_nh))
```

```{r}
library(tidyverse)
library(tidytext)
nh_word_count <- nh_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
nh_con_tidy_nostop <- nh_con_tidy %>%
 anti_join(stop_words) 
nh_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) %>%
  filter(!word%in%c("(art.", " "))
```

## New Jersey

```{r}
library(rvest)
library(dplyr)

nj_url <- "https://avalon.law.yale.edu/18th_century/nj15.asp"
nj_html <- read_html(nj_url)

nj_text <- html_text(nj_html)

nj_con <- data.frame(word = unlist(strsplit(nj_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude_nj <- c(1:55, 2524:2889)

nj_con_tidy <- nj_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude_nj))
```

```{r}
library(tidyverse)
library(tidytext)
nj_word_count <- nj_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
nj_con_tidy_nostop <- nj_con_tidy %>%
 anti_join(stop_words) 
nj_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) %>%
  filter(!word%in%c("(art.", " "))
```

## New York

```{r}

library(rvest)
library(dplyr)

ny_url <- "https://avalon.law.yale.edu/18th_century/ny01.asp"
ny_html <- read_html(ny_url)

ny_text <- html_text(ny_html)

ny_con <- data.frame(word = unlist(strsplit(ny_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude <- c(1:68, 7813:8781)

ny_con_tidy <- ny_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))


```

```{r}
library(tidyverse)
library(tidytext)

ny_word_count <- ny_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
ny_con_tidy_nostop <- ny_con_tidy %>%
 anti_join(stop_words) 
ny_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n)
```

## North Carolina

```{r}

library(rvest)
library(dplyr)

nc_url <- "https://avalon.law.yale.edu/18th_century/nc07.asp"
nc_html <- read_html(nc_url)

nc_text <- html_text(nc_html)

nc_con <- data.frame(word = unlist(strsplit(nc_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude <- c(1:58, 3991:4231)

nc_con_tidy <- nc_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))
```

```{r}
library(tidyverse)
library(tidytext)
nc_word_count <- nc_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
nc_con_tidy_nostop <- nc_con_tidy %>%
 anti_join(stop_words) 
nc_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) %>%
  filter(!word%in%c("(--", " "))
```

## Pennsylvania

```{r}

library(rvest)
library(dplyr)

pa_url <- "https://avalon.law.yale.edu/18th_century/pa08.asp"
pa_html <- read_html(pa_url)

pa_text <- html_text(pa_html)

pa_con <- data.frame(word = unlist(strsplit(pa_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude <- c(1:57, 6196:6533)

pa_con_tidy <- pa_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))
```

```{r}
library(tidyverse)
library(tidytext)
pa_word_count <- pa_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
pa_con_tidy_nostop <- pa_con_tidy %>%
 anti_join(stop_words) 
pa_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) %>%
  filter(!word%in%c("(--", " "))
```

## Rhode Island

```{r}
ri_url <- "https://www.wordservice.org/State%20Constitutions/usa1031.htm"
ri_html <- read_html(ri_url)

ri_text <- html_text(ri_html)

ri_con <- data.frame(word = unlist(strsplit(ri_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 


rows_to_exclude_ri <- c(1:200, 7322:7331)

ri_con_tidy <- ri_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude_ri))
```

```{r}
library(tidyverse)
library(tidytext)
ri_word_count <- ri_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
ri_con_tidy_nostop <- ri_con_tidy %>%
 anti_join(stop_words) 
ri_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) %>%
  filter(!word%in%c("(--", " "))
#WHY SPACE
```

## South Carolina

```{r}
library(rvest)
library(dplyr)

sc_url <- "https://avalon.law.yale.edu/18th_century/sc02.asp"
sc_html <- read_html(sc_url)

sc_text <- html_text(sc_html)

sc_con <- data.frame(word = unlist(strsplit(sc_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude <- c(1:58, 5639:5880)

sc_con_tidy <- sc_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))
```

```{r}
library(tidyverse)
library(tidytext)
sc_word_count <- sc_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
sc_con_tidy_nostop <- sc_con_tidy %>%
 anti_join(stop_words) 
nc_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) %>%
  filter(!word%in%c("(--", " "))
```

## Virginia

```{r}
va_url <- "https://www.wordservice.org/State%20Constitutions/usa1025.htm"
va_html <- read_html(va_url)

va_text <- html_text(va_html)

va_con <- data.frame(word = unlist(strsplit(va_text, "\\s+"))) %>%
  filter(word != "")  %>%
  mutate(word = str_replace_all(word, "[[:punct:][:space:]]+", "")) 

rows_to_exclude_va <- c(1:201, 3680:3689)

va_con_tidy <- va_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude_va))
```

```{r}
library(tidyverse)
library(tidytext)
va_word_count <- va_con_tidy %>%
  filter(word %in%
  c("freedom", "liberty", "welfare", "consent", "prohibit", "equality", "rights")) %>%
  count(word)

data("stop_words")
va_con_tidy_nostop <- va_con_tidy %>%
 anti_join(stop_words) 
va_con_tidy_nostop %>%
  count(word, sort = TRUE) %>%
    slice_max(n = 20, order_by = n) %>%
  filter(!word%in%c("(--", " "))
```
