---
title: "State_constitutions"
format: html
editor: visual
---

## List Of States

Connecticut (Basil-Anne)

Delaware: <https://avalon.law.yale.edu/18th_century/de02.asp> (Basil-Anne)

Georgia: <https://avalon.law.yale.edu/18th_century/ga02.asp> (Katie)

Maryland: <https://avalon.law.yale.edu/17th_century/ma02.asp> (Katie)

Massachusetts: (Basil-Anne)

New Hampshire: <https://avalon.law.yale.edu/18th_century/nh09.asp> (Katie)

New Jersey: <https://avalon.law.yale.edu/18th_century/nj15.asp> (Katie)

New York: <https://avalon.law.yale.edu/18th_century/ny01.asp> (Cassie)

North Carolina: <https://avalon.law.yale.edu/18th_century/nc07.asp> (Cassie)

Pennsylvania: <https://avalon.law.yale.edu/18th_century/pa08.asp> (Cassie)

Rhode Island: (Basil-Anne)

South Carolina: <https://avalon.law.yale.edu/18th_century/sc02.asp> (Cassie)

Virginia: (Basil-Anne)

## Connecticut

```{r}

```

## Delaware

```{r}
library(rvest)
library(dplyr)

de_url <- "https://avalon.law.yale.edu/18th_century/de02.asp"
de_html <- read_html(de_url)

de_text <- html_text(de_html)

de_con <- data.frame(word = unlist(strsplit(de_text, "\\s+"))) %>%
  filter(word != "")  

rows_to_exclude <- c(1:54, 3721:3796)

de_con_tidy <- de_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))

```

## Georgia

```{r}

```

## Maryland

```{r}

```

## Massachusetts

```{r}

```

## New Hampshire

```{r}

```

## New Jersey

```{r}

```

## New York

```{r}

library(rvest)
library(dplyr)

ny_url <- "https://avalon.law.yale.edu/18th_century/ny01.asp"
ny_html <- read_html(ny_url)

ny_text <- html_text(ny_html)

ny_con <- data.frame(word = unlist(strsplit(ny_text, "\\s+"))) %>%
  filter(word != "")  

rows_to_exclude <- c(1:68, 7813:8781)

ny_con_tidy <- ny_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))


```

## North Carolina

```{r}

library(rvest)
library(dplyr)

nc_url <- "https://avalon.law.yale.edu/18th_century/nc07.asp"
nc_html <- read_html(nc_url)

nc_text <- html_text(nc_html)

nc_con <- data.frame(word = unlist(strsplit(nc_text, "\\s+"))) %>%
  filter(word != "")  

rows_to_exclude <- c(1:58, 3991:4231)

nc_con_tidy <- nc_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))
```

## Pennsylvania

```{r}

library(rvest)
library(dplyr)

pa_url <- "https://avalon.law.yale.edu/18th_century/pa08.asp"
pa_html <- read_html(pa_url)

pa_text <- html_text(pa_html)

pa_con <- data.frame(word = unlist(strsplit(pa_text, "\\s+"))) %>%
  filter(word != "")  

rows_to_exclude <- c(1:57, 6196:6533)

pa_con_tidy <- pa_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))
```

## Rhode Island

```{r}

```

## South Carolina

```{r}
library(rvest)
library(dplyr)

sc_url <- "https://avalon.law.yale.edu/18th_century/sc02.asp"
sc_html <- read_html(sc_url)

sc_text <- html_text(sc_html)

sc_con <- data.frame(word = unlist(strsplit(sc_text, "\\s+"))) %>%
  filter(word != "")  

rows_to_exclude <- c(1:58, 5639:5880)

sc_con_tidy <- sc_con %>%
  mutate(word = tolower(word)) %>%
  filter(!(row_number() %in% rows_to_exclude))
```

## Virginia

```{r}

```

## 
